---
title: "Shapes"
author: "Michael Sumner"
date: "20/09/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=7, fig.height = 7)
```

# Shapes

This is not a shapefile. 

It's a `SpatialPolygonsDataFrame`, rendered in a particular way using the R programming language. 

```{r}
library(aceecostats)
library(sp)
plot(aes_region_simple, col = aes_region_simple$colour)
```

It can be rendered in various ways. 

```{r}
library(anglr)

mesh <- anglr(aes_region_simple)
plot(mesh)
rgl::rglwidget()
```

```{r}
library(anglr)
rgl::rgl.clear()
mesh <- anglr(aes_region_simple)
plot(globe(mesh))
rgl::rglwidget()
```

```{r}
library(mapview)
mapview(aes_region_ll, col.regions = aes_region_ll$colour) # viridis::viridis(nrow(aes_region_ll)))
```

Finally, we can nowadays actually edit or create our own drawings interactively, but this is still 
an early stage. 

```{r}
library(mapedit)
```

# Simple shape

A map of Antarctica is pretty complicated, so let's take it back a little. 

```{r}
library(silicate)
data("minimal_mesh")
library(sf)
print(minimal_mesh)
plot(minimal_mesh)
```


This simple situation hides a lot of problems. 

## First problem

It's pretty complicated. 

```{r}
str(unclass(minimal_mesh$geom))
```

## Second problem

There are three shapes here, but only two values.  (One of the shapes is a hole). 

```{r}
minimal_mesh$a
```
## Third problem

There are shared-elements between these two objects, two coordinates and one edge. But how can we know this? 

```{r}
op <- par(xpd = NA)
plot(minimal_mesh, col = NA)
ring1 <- minimal_mesh$geom[[1]][[1]][[1]]
points(ring1)
text(ring1, label = sprintf("%s,%s", ring1[, 1], ring1[, 2]), pos = 2, adj = 3, col = "dodgerblue")
ring2 <- minimal_mesh$geom[[2]][[1]][[1]]
points(ring2)
text(ring2, label = sprintf("%s,%s", ring2[, 1], ring2[, 2]), pos = 4, adj = 3, col = "firebrick")

par(op)
```


## Standard algorithms don't know about the shapes

```{r}
## maybe use the sc example instead?
plot(minimal_mesh, col = NA, lwd = 4)
plot(st_triangulate(minimal_mesh), add = TRUE, col = NA, border = "red")
```


# Raster data

Why are polygons interesting? Because they are *arbitrary partitions in space* into which we can 
summarize or record data. Raster data are interesting because they partition space into *standard* or *finite elements*, essentially small simple pieces that can be used to perform more complicated aggregate tasks. 

We can summarize raster data into polygon data, it's a standard facility. 

```{r}
library(raadtools)
sst <- readsst(as.Date("2017-09-01") + 0:17, xylim = extent(aes_region_ll))
#saveRDS(sst, file = "ghrsst.rds")
ex_sst <- extract(sst, aes_region_ll)
```


## Return to the blocky triangles in original

- resize the triangles for a smoother curve

- elevate with bathymetry

- show the North Carolina example





